Quantifying fish range shifts across poorly defined management boundaries

### 2021-11-29 Scripts/manuscript_acrossboundaries.Rmd
Further changes to manuscript

---
title: "Quantifying fish range shifts across poorly defined management boundaries"
subtitle: "DRAFT. Target journal *PlosOne*"
author: "Palacios-Abrantes Juliano, Crosson Scott, Dumas Chris, Fujita Rod, Levine Arielle, Longo Catherine, Jensen Olaf"
output: 
  bookdown::word_document2:
    number_section: no
    toc: no
---

@@

>>>>

---
title: "Quantifying fish range shifts across poorly defined management boundaries"
author: "DRAFT. Target journal *PlosOne*"
subtitle: "Juliano Palacios-Abrantes*^1^, Scott Crosson^2^, Chris Dumas^3^, Rod Fujita^4^, Arielle Levine^5^, Catherine Longo^6^, Olaf Jensen^1^"
date: "Affiliations: ^1^Center for Limnology, University of Wisconsin-Madison, US. ^2^National Oceanic and Atmospheric Administration, US. ^3^University of North Carolina Wilmington, US. ^4^Rod Fujita, Environmental Defense Fund, US. ^5^San Diego State University, US. ^6^Marine Stewardship Council, UK."
output: 
  bookdown::word_document2:
    number_section: no
    toc: no
    latex_engine: xelatex
bibliography: ../References/Across_Bound_Ref.bib
csl: ../References/plos-one.csl
header-includes:
  - \usepackage{setspace}
  - \usepackage{caption}
  - \usepackage[left]{lineno} # for numbers in lines
  - \usepackage{float} # Use the 'float' package
  - \captionsetup[figure]{name = Fig}
  - \floatplacement{figure}{H}
---

@@

**WANCHEESE NORTH CAROLINA FOR BLACK SEA BASS**
